### 2019-04-02 Model.tex
Updates from Overleaf

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. 
Using Jensen’s inequality, one can show that the total probability mass of the objective in Eq. 3 is less than or equal to the true amount of probability mass (Eq. 5); In this sense, previous work is optimizing a bound on the log-likelihood, while we are optimizing it directly.

If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low in Eq. 3. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up sequence (permutation) probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set. Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). The ``ALL'' flag determines if the sequences can terminate with a partial subset of labels (as called in Algorithm 3 line 2 ) or a full set is required (as called in Algorithm 3 line 7 and Algorithm 2 line 4). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

>>>>

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. 
Using Jensen’s inequality, one can show that the total probability mass of the objective in Eq. \ref{eq:wrong_obj} is less than or equal to the true amount of probability mass (Eq. \ref{eq:right_obj}); In this sense, previous work is optimizing a bound on the log-likelihood, while we are optimizing it directly.

If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low in objective (\ref{eq:wrong_obj}). In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

\begin{algorithm}[ht]
    \SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up sequence (permutation) probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set. Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). The ``ALL'' flag determines if the sequences can terminate with a partial subset of labels (as called in Algorithm~\ref{alg:test} line 2 ) or a full set is required (as called in Algorithm~\ref{alg:train_beam} line 4 and Algorithm~\ref{alg:test} line 7). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

### 2019-04-02 conclusion.tex
Updates from Overleaf

\section{Conclusion}
In this work, we present an adaptation of RNN sequence models to the problem of multi-label classification for text. RNN only directly defines probabilities for sequences, but not for sets. Different from previous approaches, which either transform a set to a sequence in some pre-specified order, or relate the sequence probability to the set probability in some ad hoc way, our formulation is derived from a principled notion of set probability. We define the set probability as the sum of all corresponding sequence permutation probabilities. We derive a new training objective that maximizes the set probability and a new prediction objective that finds the most probable set. These new objectives are theoretically more appealing than existing ones, because they give the RNN model more freedom to automatically discover and utilize the best label orders.\kechen{or we can move this to the intro: There’s a good analogy to be made in §2 to most probable parse vs most probable sentence in parsing. One sentence can be represented by multiple parses, and one set can be represented by many orderings. Extracting what we want would require marginalizing over structures (as you explain later). There’s also the idea of Viterbi EM versus regular EM; the former only uses the best structure.}
 % We develop efficient procedures to tackle the computations difficulties involved in training and prediction. Experiments on benchmark data sets demonstrate that our method outperforms state-of-the-art methods for this task, especially on rare labels.

>>>>

\section{Conclusion}
In this work, we present an adaptation of RNN sequence models to the problem of multi-label classification for text. RNN only directly defines probabilities for sequences, but not for sets. Different from previous approaches, which either transform a set to a sequence in some pre-specified order, or relate the sequence probability to the set probability in some ad hoc way, our formulation is derived from a principled notion of set probability. We define the set probability as the sum of all corresponding sequence permutation probabilities. We derive a new training objective that maximizes the set probability and a new prediction objective that finds the most probable set. These new objectives are theoretically more appealing than existing ones, because they give the RNN model more freedom to automatically discover and utilize the best label orders.%\kechen{or we can move this to the intro: There’s a good analogy to be made in §2 to most probable parse vs most probable sentence in parsing. One sentence can be represented by multiple parses, and one set can be represented by many orderings. Extracting what we want would require marginalizing over structures (as you explain later). There’s also the idea of Viterbi EM versus regular EM; the former only uses the best structure.}
 % We develop efficient procedures to tackle the computations difficulties involved in training and prediction. Experiments on benchmark data sets demonstrate that our method outperforms state-of-the-art methods for this task, especially on rare labels.

### 2019-04-02 results.tex
Updates from Overleaf

We test our proposed set-RNN method on 4 real-world datasets, RCV1-v2, Slashdot, TheGuardian, and Arxiv Academic Paper Dataset (AAPD) \cite{DBLP:journals/corr/abs-1806-04822}. We take the public RCV1-v2 release\footnote{\scriptsize\url{http://www.ai.mit.edu/projects/jmlr/papers/volume5/lewis04a/lyrl2004_rcv1v2_README.htm}} and randomly sample 50,000 documents. We crawl Slashdot and TheGuardian documents from their websites\footnote{\scriptsize Slashdot: \url{https://slashdot.org/} Note that there is another public Slashdot multi-label dataset \cite{read2009classifier} but we do not use that one because it is quite small. TheGuardian: \url{https://www.theguardian.com}  
} and treat the official editor tags as ground truth. We also gather a list of user tags\footnote{\scriptsize \url{www.zubiaga.org/datasets/socialbm0311/}} for each document and treat them as additional features. For AAPD dataset, we follow the same train/test split as in \cite{DBLP:journals/corr/abs-1806-04822}. Table \ref{tab:stats} contains statistics of these four datasets. 
\begin{table}[h]
	\resizebox{1.01\columnwidth}{!}{%resize the table
\begin{tabular}{|l|c|c|c|c|c|c|}
  \hline
  Data & \#train & \#test & cardinality & \#labels & doc length  \\
  \hline
  Slashdot & 19,258 & 4,814& 4.15& 291&64 \\
  RCV1-v2 & 40,000& 10,000&  3.17& 101&121 \\
  TheGuardian & 37,638 & 9,409 & 7.41& 1,527&505 \\
  AAPD & 53,840 & 1,000 & 2.41& 54 & 163 \\
  \hline
\end{tabular}
}
\caption{\fontsize{10}{12}\selectfont  Statistics of the datasets.}\label{tab:stats}
\end{table}

@@

 We implement  RNN with attention using \textsc{tensorflow-1.4.0} \cite{DBLP:conf/osdi/AbadiBCCDDDGIIK16}. The dynamic function for  RNNs is chosen to be Gated recurrent units (GRU) with  2 layers and at most 50 units in decoder. The  size of the GRU unit is 300. We set dropout rate to 0.3, and train the model with Adam optimizer \cite{DBLP:journals/corr/KingmaB14} with learning rate $0.0005$. Beam size is set to be 12 at both training and inference stages. We adopt \emph{label-F1} (average F1 over labels) and \emph{instance-F1} (average F1 over instances) as our main evaluation metrics, as defined below:

@@

Our method performs the best in all metrics on all datasets (except hamming loss on AAPD, see table \ref{table3}). All RNN based methods perform better than traditional methods BR, BR-support and PCC. Among the Vinyals-RNN variants, Vinyals-RNN-max and Vinyals-sample work the best and have similar performance. However, they have to be initialized by Vinyals-RNN-uniform. Otherwise, the training gets stuck in early stage and the performance degrades significantly. One can see the clear degradation by comparing the Vinyals-RNN-max row (with initialization) with the Vinyals-RNN-max-direct row (without initialization). By contrast, our training objective in set-RNN does not suffer from this issue and can serve as a stable stand alone training objective.

@@

\subsection{Analysis: Sequence Probability Dsitribution}
This motivates us to check how sharply (or uniformly) distributed the probabilities are over different sequence permutations of the predicted set. We first normalize these sequence probabilities related to the predicted set and then compute the entropy. To make predictions with different set sizes (and hence different number of sequence permutations) comparable, we further divide the entropy by the logarithm of number of sequences. Smaller entropy values indicate a sharper distributions. The results are shown in Figure~\ref{fig:entropy}.

>>>>

We test our proposed set-RNN method on 4 real-world datasets, RCV1-v2, Slashdot, TheGuardian, and Arxiv Academic Paper Dataset (AAPD) \cite{DBLP:journals/corr/abs-1806-04822}. We take the public RCV1-v2 release\footnote{\scriptsize\url{http://www.ai.mit.edu/projects/jmlr/papers/volume5/lewis04a/lyrl2004_rcv1v2_README.htm}} and randomly sample 50,000 documents. We crawl Slashdot and TheGuardian documents from their websites\footnote{\scriptsize Slashdot: \url{https://slashdot.org/} Note that there is another public Slashdot multi-label dataset \cite{read2009classifier} but we do not use that one because it is quite small. TheGuardian: \url{https://www.theguardian.com}  
} and treat the official editor tags as ground truth. We also gather a list of user tags\footnote{\scriptsize \url{www.zubiaga.org/datasets/socialbm0311/}} for each document and treat them as additional features. For AAPD dataset, we follow the same train/test split as in \cite{DBLP:journals/corr/abs-1806-04822}. Table \ref{tab:stats} contains statistics of these four datasets. 
\begin{table}[h]
	\resizebox{1.01\columnwidth}{!}{%resize the table
\begin{tabular}{|l|c|c|c|c|c|c|}
  \hline
  Data & \#Train & \#Test & Cardinality & \#Labels & Doc length  \\
  \hline
  Slashdot & 19,258 & 4,814& 4.15& 291&64 \\
  RCV1-v2 & 40,000& 10,000&  3.17& 101&121 \\
  TheGuardian & 37,638 & 9,409 & 7.41& 1,527&505 \\
  AAPD & 53,840 & 1,000 & 2.41& 54 & 163 \\
  \hline
\end{tabular}
}
\caption{\fontsize{10}{12}\selectfont  Statistics of the datasets.}\label{tab:stats}
\end{table}

@@

 We implement RNNs with attention using \textsc{tensorflow-1.4.0} \cite{DBLP:conf/osdi/AbadiBCCDDDGIIK16}. The dynamic function for  RNNs is chosen to be Gated recurrent units (GRU) with  2 layers and at most 50 units in decoder. The  size of the GRU unit is 300. We set dropout rate to 0.3, and train the model with Adam optimizer \cite{DBLP:journals/corr/KingmaB14} with learning rate $0.0005$. Beam size is set to be 12 at both training and inference stages. We adopt \emph{label-F1} (average F1 over labels) and \emph{instance-F1} (average F1 over instances) as our main evaluation metrics, as defined below:

@@

Our method performs the best in all metrics on all datasets (except hamming loss on AAPD, see table \ref{tab:main}). In general, RNN based methods perform better than traditional methods BR, BR-support and PCC. Among the Vinyals-RNN variants, Vinyals-RNN-max and Vinyals-sample work the best and have similar performance. However, they have to be initialized by Vinyals-RNN-uniform. Otherwise, the training gets stuck in early stage and the performance degrades significantly. One can see the clear degradation by comparing the Vinyals-RNN-max row (with initialization) with the Vinyals-RNN-max-direct row (without initialization). By contrast, our training objective in set-RNN does not suffer from this issue and can serve as a stable stand alone training objective.

@@

\subsection{Analysis: Sequence Probability Dsitribution}
Results in Table~\ref{table_prediction} motivates us to check how sharply (or uniformly) distributed the probabilities are over different sequence permutations of the predicted set. We first normalize these sequence probabilities related to the predicted set and then compute the entropy. To make predictions with different set sizes (and hence different number of sequence permutations) comparable, we further divide the entropy by the logarithm of number of sequences. Smaller entropy values indicate a sharper distributions. The results are shown in Figure~\ref{fig:entropy}.
